% 31-affirmations-close.xhtml
% Type: affirmation

{Closing}

\hypertarget{the-artists-manifesto}{%
\section{The Artist\textquotesingle s Manifesto}\label{the-artists-manifesto}}

\hypertarget{your-professional-declaration}{%
\subsection{Your Professional Declaration}\label{your-professional-declaration}}

Read each statement aloud. Let these truths settle into your identity as an artist.

\hypertarget{i-am-a-value-multiplier.}{%
\subsubsection{I am a value multiplier.}\label{i-am-a-value-multiplier.}}

My work transforms not just hair, but confidence, identity, and self-worth. Every client who sits in my chair leaves carrying something invisible but invaluable.

\hypertarget{i-lead-with-integrity.}{%
\subsubsection{I lead with integrity.}\label{i-lead-with-integrity.}}

My influence extends beyond the chair to my community. I set standards through my actions, not just my words. I am honest about what I know and humble about what I\textquotesingle m still learning.

\hypertarget{i-honor-my-craft-and-myself.}{%
\subsubsection{I honor my craft and myself.}\label{i-honor-my-craft-and-myself.}}

My boundaries protect my creativity. My prices reflect my worth. My time is sacred. I cannot pour from an empty cup.

\hypertarget{your-personal-manifesto}{%
\subsubsection{\texorpdfstring{{✦} Your Personal Manifesto}{✦ Your Personal Manifesto}}\label{your-personal-manifesto}}

In your own words, declare who you are and what you stand for:

\hypertarget{signed}{%
\paragraph{Signed}\label{signed}}

\hypertarget{date}{%
\paragraph{Date}\label{date}}

{Curls \& Contemplation}
{The Artist\textquotesingle s Manifesto}
