% 44-bibliography.xhtml
% Type: bibliography

\hypertarget{bibliography}{%
\section{BIBLIOGRAPHY}\label{bibliography}}

\begin{itemize}
\tightlist
\item
  Abboud, G. "The Future of Braiding: StrandBuilder's Digital Braiding App." \emph{Essence}, 2020. \url{https://www.essence.com/hair/strandbuilder-digital-braiding-app/}.
\item
  Advance Partners. "Four Key Components to Financial Sustainability." 2023. \url{https://www.advancepartners.com/blog/four-key-components-to-financial-sustainability/}.
\item
  AIIR Professional. "Your Stay-at-Home Toolkit for Hair Wellness and Holistic Self-Care." 2023. \url{https://aiirprofessional.com/blogs/premium/your-stay-at-home-toolkit-for-hair-wellness-and-holistic-self-care}.
\item
  Aksoy, M., et al. "The Impact of Aesthetic Changes on the Environmental Adaptation of Individuals." \emph{Journal of Health Sciences}, vol. 15, no. 2, 2023. doi:10.14687/JHS.V15I2.5307.
\item
  Algonquin College. "Hairstyling." 2023. \url{https://www.algonquincollege.com/business-hospitality/program/hairstyling/}.
\item
  Allen, T. D., L. T. Eby, M. L. Poteet, E. Lentz, and L. Lima. "Career Benefits Associated with Mentoring for Protégés: A Meta-Analysis." \emph{Journal of Applied Psychology}, 2004. \url{https://psycnet.apa.org/fulltext/2004-15660-007.html}.
\item
  Allure. "Jen Atkin: From Couch to Celebrity." 2019. \url{https://www.allure.com/story/jen-atkin-profile}.
\item
  Allure. "Kim Kimble: Celebrating Natural Hair." 2018. \url{https://www.allure.com/story/kim-kimble-interview}.
\item
  Allure. "The Secret Behind Rihanna\textquotesingle s Iconic Hairstyles: Meet Ursula Stephen." April 18, 2017. \url{https://www.allure.com/story/ursula-stephen-hairstylist-rihanna}.
\item
  Allure. "Tokyo Stylez Tells All." 2023. \url{https://www.allure.com}.
\item
  American Association of Cosmetology Schools. "Innovative Training for Diverse Hair Types." 2019. Accessed March 8, 2025. \url{https://www.aacs.org/initiatives/diverse-hair-training}.
\item
  American College of Sports Medicine. "Benefits of Stretching and Strength Training." 2021. \url{https://www.acsm.org}.
\item
  American Psychological Association. "Building Resilience: How to Bounce Back." 2019. Accessed March 8, 2025. \url{https://www.apa.org/topics/resilience}.
\item
  American Psychological Association. "Mind/Body Health: Meditation." 2020. \url{https://www.apa.org/topics/mindfulness/meditation}.
\item
  American Psychological Association. "The Importance of Setting Boundaries for Mental Health." 2020. Accessed March 8, 2025. \url{https://www.apa.org}.
\item
  American Salon. "Career Development for Hairstylists." 2021. \url{https://www.americansalon.com/career-development}.
\item
  American Salon. "How to Prepare for a Master Portfolio Review." 2022. Accessed March 8, 2025. \url{https://www.americansalon.com}.
\item
  American Salon. "Jayne Matthews on Small-Group Networking." n.d. Accessed March 8, 2025. \url{https://www.americansalon.com}.
\item
  Angelou, M. \emph{I Know Why the Caged Bird Sings}. Random House, 1969.
\item
  Annunziata, Sherri. \emph{The Art and Science of Hairstyling}. Routledge, 2019.
\item
  Appleton, C. "Reinventing Through Collaboration." {[}Speech transcript{]}. NAHA Thrive Conference, Las Vegas, NV, November 2, 2022.
\item
  Atkin, J. "The Generosity Mindset Behind Networking." {[}Interview{]}. February 8, 2023.
\item
  Atkin, Jennifer. \emph{Blowing My Way to the Top: How to Break the Rules, Find Your Purpose, and Create the Life and Career You Deserve}. New York: Harper Wave, 2020.
\item
  AVACare Medical. "6 Exercises for Hairstylists to Prevent Injury." April 23, 2021. \url{https://avacaremedical.com/articles/exercises-for-hairstylists/}.
\item
  Aveda. "Aveda Education." 2023. Accessed March 8, 2025. \url{https://www.aveda.com/education}.
\item
  Aveda. "Discover our Corporate Social Responsibility." n.d. \url{https://www.aveda.com/csr-initiatives}.
\item
  Aveda. "Learn how we give back to the community." n.d. \url{https://www.aveda.com/mission-giving-back}.
\item
  Aveda. "Learn more about our environmental initiatives." n.d. \url{https://www.aveda.com/carbon-neutrality-green-initiatives}.
\item
  Aveda. "Living Aveda Blog - 5 Ways We Care For The Environment." n.d. \url{https://www.aveda.com/living-aveda-article-our-sustainable-practices}.
\item
  Aveda Institutes. "Curriculum Overview: Textured Hair and Product Science." 2020. Accessed March 8, 2025. \url{https://www.avedainstitutes.edu/programs/textured-hair}.
\item
  Avenue Five Institute. "The Importance of Advanced Education for Hair Stylists." 2023. \url{https://www.avenuefive.edu/the-importance-of-advanced-education-for-hair-stylists/}.
\item
  Aweto, H.A., et al. "Ergonomic Hazards and Musculoskeletal Disorders among Hairstylists." \emph{Safety and Health at Work}, 13(3), 2022: 285-292. doi:10.1016/j.shaw.2022.04.004.
\item
  Aweto, H.A., et al. "Prevalence of Work-Related Musculoskeletal Disorders Among Hairstylists in Nigeria and Its Association with Workplace Ergonomic Factors." \emph{International Journal of Environmental Research and Public Health}, 20(4), 2023: 2785.
\item
  Baird, V. "Hair as a Marker of Identity in Hmong American Films: The Cultural Significance of Hair." \emph{Journal of American Folklore Research}, vol. 10, no. 1, 2023. doi:10.5325/jafrireli.10.1.0020.
\item
  Bandura, Albert. \emph{Self-Efficacy: The Exercise of Control}. New York: Worth Publishers, 1997. \url{https://www.uky.edu/~eushe2/Bandura/Bandura1997EP.pdf}.
\item
  Banka, N., et al. "The Psychological Impact of Hair Loss among Men and Women." \emph{International Journal of Dermatology}, vol. 51, no. 10, 2022. doi:10.1111/j.1529-8019.2012.01506.x.
\item
  Banks, C. "Inclusive Hair Care: Addressing Accessibility in Salons." \emph{Salon Today}, 2020. \url{https://www.salontoday.com/inclusive-hair-care-accessibility}.
\item
  Beauty Innovation Institute. "Getting Started with AI in Beauty: A Beginner\textquotesingle s Guide." 2022. \url{https://www.beautyinnovation.org}.
\item
  Beauty Matter. "The Rise of Sustainability in Salons." 2023. \url{https://beautymatter.com/articles/the-rise-of-sustainability-salons}.
\item
  BeautyTech Review. "Bread Beauty Supply: From Kitchen Startup to Eco-Conscious Powerhouse." June 15, 2021. \url{https://www.beautytechreview.com/bread-beauty-supply-eco}.
\item
  Behind the Chair. "The Benefits of Shadowing in Hairstyling." 2021. \url{https://www.behindthechair.com}.
\item
  Behind the Chair. "Mentorship in Freelance Hairstyling: Success Stories." 2018. \url{https://www.behindthechair.com}.
\item
  Behind The Chair Magazine. "Vernon François Joins Ulta Beauty Pro Team of Industry-Leading Artists \& Educators." April 14, 2023. \url{https://behindthechair.com}.
\item
  Belleza Hairstyling. "Empowering Self-Care: Why Women Should Prioritize Hair Care for Mental Well-being." 2023. \url{https://belleza-hairstyling.com/blogs/news/empowering-self-care-why-women-should-prioritize-hair-care-for-mental-well-being}.
\item
  Bernal, J. "Finding Your Creative Guide: A Journey Toward Mentorship." \emph{Stratton Magazine}, 2022.
\item
  Bio Ionic. "How We Highlight Sustainability." n.d. \url{https://www.bioionic.com}.
\item
  Black Women in Beauty. "Representation in the Beauty Industry." 2022. \url{https://blackwomeninbeauty.org/representation-report}.
\item
  Bosley, Rawn E., and Steven Daveluy. "A Consideration of Natural Hair Care Practices in Black Patients." \emph{Journal of Dermatological Treatment}, 2023. pubmed.ncbi.nlm.nih.gov/25750968.
\item
  Brandignity. "Hair Salon Marketing Strategies." 2016. \url{https://www.brandignity.com/2016/12/hair-salon-marketing-strategies/}.
\item
  Breslin, Marquetta. "Building a Thriving Lace Wig Business." \emph{WWD}, 2018. \url{https://wwd.com/beauty-industry-news/hair/marquetta-breslin-profile}.
\item
  Briogeo. "How We Highlight Sustainability." n.d. \url{https://briogeohair.com/pages/sustainability}.
\item
  Brown, B. \emph{Daring Greatly: How the Courage to Be Vulnerable Transforms the Way We Live, Love, Parent, and Lead}. Gotham Books, 2012.
\item
  Bundles, A\textquotesingle Lelia. \emph{On Her Own Ground: The Life and Times of Madam C.J. Walker}. New York: Alfred A. Knopf, 2001.
\item
  Burns, Kelli. \emph{Social Media: A Reference Handbook}. ABC-CLIO, 2018.
\item
  Burns, L. "The Salons Empowering Trauma Survivors Through Haircare." \emph{SF Chronicle}, December 2, 2020. \url{https://www.sfchronicle.com/}.
\item
  Byrdie. "An Interview with Celebrity Hairstylist Kim Kimble." 2017. \url{https://www.byrdie.com/kim-kimble-interview}.
\item
  Byrdie. "How amika\textquotesingle s Global Artistic Director Naeemah LaFond Is Pushing the Boundaries of Inclusivity in Beauty." n.d.
\item
  California Legislative Information. "AB-2762 Cosmetic products: safety." 2020. \url{https://leginfo.legislature.ca.gov}.
\item
  Camille Rose Naturals. "How We Highlight Sustainability." n.d. \url{https://www.camillerose.com}.
\item
  Carocci, Max. "Hair and Hair-Like Materials in Native American Textile Industries." \emph{Journal of Material Culture}, vol. 15, no. 3, 2023. doi:10.1179/174329510x12670196126485.
\item
  Cash, Thomas F., and T. A. Pruzinsky. "The Role of Physical Appearance in Shaping Self-Perception: Implications for Mental Health." \emph{Psychology and Health} (2002).
\item
  Casserly, M. "Why Hairstylists Need Their Own Online Communities." \emph{HuffPost}, March 15, 2021. \url{https://www.huffpost.com/entry/why-hairstylists-need-thei_b_9649952}.
\item
  Chowdhury, S. "Strategic Networking for Product Managers." \emph{Mind the Product}, 2020.
\item
  Christensen, Clayton M. \emph{The Innovator\textquotesingle s Dilemma: When New Technologies Cause Great Firms to Fail}. Boston: Harvard Business Review Press, 1997.
\item
  Coffey, Tabatha. \emph{It\textquotesingle s Not Really About the Hair}. New York: Penguin Group, 2006.
\item
  Cohen, S. "The Physical Toll of Being a Hairstylist." \emph{The New York Times}, April 6, 2020. \url{https://www.nytimes.com/2020/04/06/well/live/hairstylists-injuries-pain.html}.
\item
  Congress.gov. "H.R.5017 - Natural Cosmetics Act." 2019. \url{https://www.congress.gov}.
\item
  Corcodilos, N. "80 Percent of Jobs Are Not Advertised: Networking Really Works." \emph{Ask The Headhunter}, April 3, 2022.
\item
  Creative Head Magazine. "Embracing Diversity: The Power of Inclusive Education in Textured Hair Styling." 2023. \url{https://creativeheadmag.com/embracing-diversity-the-power-of-inclusive-education-in-textured-hair-styling/}.
\item
  CROWN Coalition, The. "About the CROWN Act." 2020. Accessed March 8, 2025. \url{https://www.thecrowncoalition.org/about}.
\item
  Cutting, Paul, Richard Ross, and Robert Hill. \emph{Hairdressing: Theory, Science and Practice}. Reading, MA: Addison-Wesley, 1988.
\item
  Davines. "For You And For The Planet." n.d. \url{https://us.davines.com/pages/for-you-and-for-the-planet}.
\item
  Davines. "How We Highlight Sustainability." n.d. \url{https://us.davines.com/blogs/news/how-we-highlight-sustainability}.
\item
  Davis, M. \emph{The Stylist's Guide to Anti-Inflammatory Nutrition}. Hairgenius Publications, 2021.
\item
  Deloitte. "The Future of Beauty: Thriving in Turbulent Times." 2023. \url{https://www2.deloitte.com/us/en/pages/consumer-business/articles/future-of-beauty-thriving-in-turbulent-times.html}.
\item
  DevaCurl. "DevaCut Training Program." 2021. Accessed March 8, 2025. \url{https://www.devacurl.com/professionals/devacut}.
\item
  Digital Wellness Institute. "Social Media Wellness for the Salon Professional." 2023. \url{https://www.digitalwellnessinstitute.com/salon-pro}.
\item
  Diversity in Design Magazine. "Inclusive Salon Design: Celebrating Diversity Through Décor." October 5, 2020. \url{https://www.diversityindesignmag.com/inclusive-salon-design}.
\item
  Doran, George T. "There\textquotesingle s a S.M.A.R.T. Way to Write Management\textquotesingle s Goals and Objectives." \emph{Management Review} 70, no. 11 (1981): 35--36.
\item
  Dubois, T. \emph{Sacred Strands: Revering Hair Across Indigenous Cultures}. University of New Mexico Press, 2021.
\item
  Dweck, Carol S. \emph{Mindset: The New Psychology of Success}. New York: Random House, 2006.
\item
  Dyson. "Dyson Supersonic Hair Dryer." 2023. \url{https://www.dyson.com/hair-care/dyson-supersonic}.
\item
  Dyson. "Sustainability." n.d. \url{https://www.dyson.com/sustainability}.
\item
  Dyson, James. "How Olaplex Revolutionized Hair Repair." 2020. Accessed March 8, 2025. \url{https://www.olaplex.com}.
\item
  EcoTools. "Our Sustainability Story." n.d. \url{https://www.ecotools.com/pages/sustainability}.
\item
  EcoTools. "Our Commitment to Sustainability." 2023. Accessed March 8, 2025. \url{https://www.ecotools.com/sustainability}.
\item
  Energy Star. "Energy Efficiency for Salons." 2023. \url{https://www.energystar.gov/industry/salons}.
\item
  Entrepreneur. "Time Management Tips for Busy Professionals." 2021. \url{https://www.entrepreneur.com}.
\item
  Ericsson, Anders. \emph{Peak: Secrets from the New Science of Expertise}. Houghton Mifflin Harcourt, 2016.
\item
  Escandon, G. "How Vernon François Went From Braiding Mops to Brand Founder." \emph{Modern Salon}, May 25, 2021. \url{https://www.modernsalon.com/article/121820/how-vernon-francois-went-from-braiding-mops-to-brand-founder}.
\item
  Ess, Kristin. "Beauty Independent Interview: Kristin Ess on Digital Networking." 2019. \url{https://www.beautyindependent.com/kristin-ess-interview}.
\item
  Essence. "How Independent Stylists Are Changing the Game." 2019. \url{https://www.essence.com}.
\item
  Essence. "Ursula Stephen on Networking at New York Fashion Week." 2019. \url{https://www.essence.com/style/ursula-stephen}.
\item
  Estée Lauder Companies. "Harnessing AI for Demand Forecasting." 2021. \url{https://www.elcompanies.com/en/news-and-media}.
\item
  European Hair Professionals. "The Hair Has No Gender Project: Fostering Inclusive Beauty." 2020. \url{https://www.europeanhairpro.com/HHNG}.
\item
  Everyday Health. "Building Resilience." 2023. \url{https://www.everydayhealth.com/wellness/resilience/}.
\item
  Experticity. "The Power of Brand Partnerships in Building Consumer Trust." 2023. \url{https://experticity.com/insights/brand-partnerships-consumer-trust/}.
\item
  Farr, Liz. \emph{Hairdressing Design: A Salon Handbook}. New York: Delmar Cengage Learning, 2012.
\item
  Faster Capital. "Stay Inspired and Motivated as a Beauty Entrepreneur." 2023. \url{https://fastercapital.com/content/Stay-Inspired-and-Motivated-as-a-Beauty-Entrepreneur.html}.
\item
  Ferrazzi, Keith. \emph{Never Eat Alone: And Other Secrets to Success, One Relationship at a Time}. Currency, 2005.
\item
  Fiore, Enzo. \emph{The Hairstylist's Guide to Advanced Techniques}. Bloomsbury Publishing, 2017.
\item
  Food \& Nutrition. "Practice Self-Care with Food." 2023. \url{https://foodandnutrition.org/blogs/stone-soup/practice-self-care-with-food/}.
\item
  Forbes Business Council. "14 Effective Ways for Small Businesses to Get Involved in the Local Community." March 16, 2022. \url{https://www.forbes.com/sites/forbesbusinesscouncil/2022/03/16/14-effective-ways-for-small-businesses-to-get-involved-in-the-local-community/}.
\item
  Forbes Business Council. "Building Entrepreneurial Community: Strategies for Salon Owners." October 15, 2022. \url{https://www.forbes.com/sites/forbesbusinesscouncil/2022/10/15/building-entrepreneurial-community-strategies-for-salon-owners}.
\item
  Forbes. "10 Smart Ways to Make Self-Care a Part of Every Meal." 2017. \url{https://www.forbes.com/sites/nomanazish/2017/12/11/10-smart-ways-to-make-self-care-a-part-of-every-meal/}.
\item
  Forbes. "Diversifying Your Income Streams: A Guide for Small Business Owners." 2022. \url{https://www.forbes.com/sites/advisor/2022/09/12/diversifying-your-income-streams-a-guide-for-small-business-owners/}.
\item
  Forbes. "How Miko Branch Built Miss Jessie\textquotesingle s Into an Iconic Beauty Brand." May 1, 2020. \url{https://www.forbes.com/sites/forbesbusinesscouncil/2020/05/01/how-miko-branch-built-miss-jessies-into-an-iconic-beauty-brand/}.
\item
  Forbes. "How to Measure the ROI of Continuing Education." 2020. \url{https://www.forbes.com}.
\item
  Forbes. "The Impact of Brand Partnerships on Consumer Perception." 2022. \url{https://www.forbes.com/sites/forbesagencycouncil/2022/06/14/the-impact-of-brand-partnerships-on-consumer-perception/}.
\item
  Forbes. "The Power of Strategic Partnerships in Business Growth." 2020. \url{https://www.forbes.com}.
\item
  François, Vernon. "About Vernon François." 2023. \url{https://vernonfrancois.com}.
\item
  François, Vernon. Personal interview. 2023.
\item
  Freelancers Union. "Health Insurance Options for Freelancers." 2023. \url{https://www.freelancersunion.org}.
\item
  FreshBooks. "Why Cloud Accounting is Essential for Freelancers." 2023. \url{https://www.freshbooks.com/en-gb/cloud-accounting}.
\item
  Freund, J. "Exclusive: Federal Investigation into ChainSalons Franchise Reveals Major Violations." \emph{Modern Salon}, September 28, 2022. \url{https://www.modernsalon.com/991955/exclusive-federal-investigation-into-chainsalons-franchise-reveals-major-violations}.
\item
  Fukada, K. "The Spiritual Roots of Trendcasting." \emph{Behind the Chair}, 25(4), 2023: 62-71.
\item
  Gale, P. \emph{Your Network Is Your Net Worth: Unlock the Hidden Power of Connections for Wealth, Success, and Happiness in the Digital Age}. Atria Books, 2013.
\item
  Gcelt. "The Best Hair: Exploring the Diversity and Beauty Across Races." 2023. \url{https://gcelt.org/the-best-hair-exploring-the-diversity-and-beauty-across-races/}.
\item
  Get Neko. "Salon Leadership Skills." 2023. \url{https://www.getneko.com/salon-leadership-skills/}.
\item
  GHD. "Sustainability." n.d. \url{https://www.ghdhair.com/sustainability}.
\item
  Gibson, Ted. "Behind the Chair Interview: Ted Gibson on Networking." 2018. \url{https://behindthechair.com/interview/ted-gibson}.
\item
  Gina's College. "Diploma Programs: Hairstyling." 2023. \url{https://www.ginascollege.com/diploma-programs/hairstyling/}.
\item
  GirlGang Group. "Early Girl Gang DC: A Case Study in Sustainable Beauty." 2022. \url{https://girlganggroup.org/case-studies/early-girl-gang-dc}.
\item
  Godin, S. \emph{The Practice: Shipping Creative Work}. Penguin Books, 2022.
\item
  Godin, S. \emph{Tribes: We Need You to Lead Us}. Portfolio, 2008.
\item
  Goldstein, Daniel. "The Extended Mind in Creative Practice: How Tools Become Extensions of Ourselves." \emph{Creativity Research Journal}, 2021. \url{https://www.creativityresearchjournal.org/extended-mind}.
\item
  Goleman, Daniel. \emph{Emotional Intelligence: Why It Can Matter More Than IQ}. Bantam Books, 2005.
\item
  Goleman, Daniel. \emph{Working with Emotional Intelligence}. New York: Bantam Books, 1998.
\item
  Goruo, A. "The Sacrament of Style: Uplifting Communities Through Beauty." {[}Video{]}. CreativeLive, 2023. \url{https://www.creativelive.com/}.
\item
  Government of Ontario. "Policy Directive: Hairstyling Training Programs." 2023. \url{https://www.ontario.ca/page/policy-directive-hairstyling-training-programs}.
\item
  Granovetter, Mark. "The Strength of Weak Ties." \emph{American Journal of Sociology} 79, no. 6 (1973): 1360--1380. \url{https://www.jstor.org/stable/2776392}.
\item
  Grant, Adam. \emph{Give and Take: A Revolutionary Approach to Success}. Viking, 2013.
\item
  Green Circle Salons. "Our Sustainability Mission." n.d. \url{https://www.greencirclesalons.com/sustainability}.
\item
  Green Circle Salons. "Sustainability Impact Report." 2021. \url{https://www.greencirclesalons.com}.
\item
  Greene, L. \& Buckworth, J. "Exercise Among Hospitality Workers: A Look at Motivators and Obstacles." \emph{International Journal of Hospitality Management}, 70, 2018: 44-52.
\item
  Greener Salon \& Spa. "Our Sustainability Journey." 2022. \url{https://www.greensalonsa.com/sustainability}.
\item
  Grégoire, S. "Meditations for Workplace Well-Being." \emph{Harvard Business Review}, September 1, 2021. \url{https://hbr.org/2021/09/meditations-for-workplace-well-being}.
\item
  Grow Knoxville. "Why Healthy Hair is Important to Your Overall Well-being." 2023. \url{https://growknoxville.com/why-healthy-hair-is-important-to-your-overall-well-being/}.
\item
  Gunn, R. \emph{The Mindset of a Master Hairdresser}. Cengage Learning, 2021.
\item
  Hairbrained. "Hairbrained Mentorship Program." 2023. \url{https://www.hairbrained.me}.
\item
  Hairstyle Authority. "Low-Tension Protective Styles for Natural Hair." 2018. \url{https://www.hairstyleauthority.com/low-tension-protective-styles}.
\item
  Hairstylist Insider. "Johnny Wright: From Celebrity Cuts to Innovative Products." August 15, 2019. \url{https://www.hairstylistinsider.com/johnny-wright-celebrity-innovator}.
\item
  Hairstylist Today. "How MoKnowsHair Leveraged Digital Platforms for Growth." March 10, 2021. \url{https://www.hairstylisttoday.com/moknowshair-digital-growth}.
\item
  Hairstylist Today. "Niche Marketing for Texture Specialists." May 10, 2020. \url{https://www.hairstylisttoday.com/niche-marketing-texture}.
\item
  Harper\textquotesingle s Bazaar. "Guido Palau: The Man Behind the Modern Look." 2014. \url{https://www.harpersbazaar.com/beauty/hair}.
\item
  Harper\textquotesingle s Bazaar. "Vernon François: Championing Textured Hair." 2021. \url{https://www.harpersbazaar.com/beauty/hair}.
\item
  Harper\textquotesingle s Bazaar. "Vernon François: Redefining Beauty Standards." 2021. \url{https://www.harpersbazaar.com/beauty/hair}.
\item
  Harvard Business Review. "How Interactive Engagement Drives Customer Loyalty." 2020. \url{https://hbr.org}.
\item
  Harvard Business Review. "The Importance of Pricing Transparency." 2021. \url{https://hbr.org/2021/04/the-importance-of-pricing-transparency}.
\item
  Harvard Business Review. "The Power of Small Leadership Acts." 2020. \url{https://hbr.org}.
\item
  Harvard Business Review. "The Value of Peer Feedback in Professional Development." 2020. \url{https://hbr.org}.
\item
  Harvard T.H. Chan School of Public Health. "The Nutrition Source." 2022. \url{https://www.hsph.harvard.edu/nutritionsource}.
\item
  Healthline. "Quick Self-Care Tips." 2021. \url{https://www.healthline.com}.
\item
  Heitner, D. "How to Respond to Positive and Negative Reviews." \emph{Entrepreneur}, 2022. \url{https://www.entrepreneur.com/article/419603}.
\item
  Herman, J. "The Importance of Community Building in Digital Marketing." \emph{Harvard Business Review}, 2022. \url{https://hbr.org/2022/05/the-importance-of-community-building-in-digital-marketing}.
\item
  Hielscher, S. "The Material Interactions in Women\textquotesingle s Hair Care." \emph{Journal of Design History}, vol. 26, no. 3, 2023. doi:10.1093/JDH/EPT020.
\item
  Hill, C. "5 Tips for Networking with Integrity." \emph{Harvard Business Review}, October 15, 2020.
\item
  Hoffman, Reid, and Casnocha, Ben. \emph{The Start-up of You: Adapt to the Future, Invest in Yourself, and Transform Your Career}. Crown Business, 2012.
\item
  Holy Bible, The. New International Version. Ecclesiastes 4:9. 2011. \url{https://www.biblegateway.com/passage/?search=Ecclesiastes+4\%3A9}.
\item
  Holy Bible, The. New International Version. Proverbs 22:1. 2011. \url{https://www.biblegateway.com/passage/?search=Proverbs+22\%3A1}.
\item
  Holy Bible, The. New International Version. Proverbs 27:17. 2011. \url{https://www.biblegateway.com/passage/?search=Proverbs+27\%3A17}.
\item
  Holy Bible, The. New International Version. Psalm 78:72. 2011. \url{https://www.biblegateway.com/passage/?search=Psalm+78\%3A72}.
\item
  Honsberger, K. "Beauty From the Block: Mobile Salons Target Food Deserts." \emph{Glossy}, May 18, 2022. \url{https://www.glossy.co/beauty/beauty-from-the-block-mobile-salons-target-food-deserts}.
\item
  Hootsuite. "Social Media Marketing Best Practices." 2023. \url{https://hootsuite.com/resources/social-media-marketing}.
\item
  Hootsuite. "The State of Digital Marketing." 2023. \url{https://www.hootsuite.com/resources}.
\item
  HubSpot. "Marketing Automation Essentials." 2023. \url{https://www.hubspot.com}.
\item
  Indeed. "Hair Stylist Training." 2023. \url{https://www.indeed.com/career-advice/finding-a-job/hair-stylist-training}.
\item
  Indeed. "Self-Care at Work." 2023. \url{https://www.indeed.com/career-advice/career-development/selfcare-at-work}.
\item
  Influencer Marketing Hub. "YouTube Money Calculator." 2023. \url{https://influencermarketinghub.com/youtube-money-calculator/}.
\item
  Innersense Organic Beauty. "Innersense Impact Report." n.d. \url{https://innersensebeauty.com/pages/impact-report}.
\item
  Innersense Organic Beauty. "Innersense People and Planet." n.d. \url{https://innersensebeauty.com/pages/people-planet}.
\item
  Innersense Organic Beauty. "Innersense Sustainability Starts With All Of Us." n.d. \url{https://innersensebeauty.com/pages/sustainability-starts-with-all-of-us}.
\item
  Innersense Organic Beauty. "Innersense Sustainability." n.d. \url{https://innersensebeauty.com/pages/sustainability}.
\item
  Intuit. "QuickBooks Online." 2023. \url{https://quickbooks.intuit.com}.
\item
  Jackson, T. \emph{Against All Odds: My Fight for Stylist Rights}. Memoir Publishing Group, 2022.
\item
  Jackson, T. "Building Longevity as a Stylist." \emph{Qtique Magazine}, January 28, 2023.
\item
  Jones, Nora L., and Candrice R. Heath. "The Significance of Culturally Humble Care in Dermatology." \emph{Pediatric Dermatology}, vol. 36, no. 4, 2023. doi:10.1111/pde.14721.
\item
  Journo Portfolio. "How to Make a Showstopping Digital Portfolio for Hair Stylists \& Cosmetologists." 2023. \url{https://www.journoportfolio.com/blog/how-to-make-a-showstopping-digital-portfolio-for-hair-stylists-cosmetologists/}.
\item
  Journal of Environmental Psychology. "The Impact of Sensory-Aware Design on Customer Experience." 2019. \url{https://www.journalofenvironmentalpsychology.com/sensory-design}.
\item
  Journal of Ethnic Studies. "Traditional Hairstyling Techniques and Cultural Significance." 2020. \url{https://www.jes.org}.
\item
  Kabat-Zinn, Jon. \emph{Full Catastrophe Living: Using the Wisdom of Your Body and Mind to Face Stress, Pain, and Illness}. Delta, 1990.
\item
  Kaplan, R. "PopModerne Founder Leads Salon Safety Protests After Going Viral." \emph{PopSugar Beauty}, August 11, 2019. \url{https://www.popsugar.com/beauty/popmoderne-salon-safety-protests-46514445}.
\item
  Kaufman, Scott Barry, and Carolyn Gregoire. \emph{Wired to Create: Unraveling the Mysteries of the Creative Mind}. Penguin Books, 2016.
\item
  Keller, Kevin Lane. \emph{Strategic Brand Management}. Upper Saddle River, NJ: Prentice Hall, 2003.
\item
  Khouri, J. "Essential Salon Software 2023: The Definitive Pricing Guide." \emph{Software Advice}, 2022. \url{https://www.softwareadvice.com/salon/}.
\item
  Kimble, K. "Masterclass for Textured Hair Stylists." Interview by Refinery29, July 12, 2021.
\item
  Kinky-Curly. "About Us." n.d. \url{https://www.kinky-curly.com/about-us}.
\item
  Kram, Kathy E. \emph{Mentoring at Work: Developmental Relationships in Organizational Life}. Glenview, IL: Scott, Foresman, 1985.
\item
  Label Insight. "How Consumer Demand for Transparency is Shaping the Food Industry." 2016. \url{https://LabelInsight.com}.
\item
  Lafond, Naeemah. "Inside Amika: Naeemah Lafond\textquotesingle s Vision." \emph{Modern Salon}, 2019. \url{https://www.modernsalon.com/article/naeemah-lafond}.
\item
  Lafond, N. \emph{The Geometry of Wholeness: Rediscovering Mastery Through Patience}. NY: North Star Publishing, 2021.
\item
  Larré, F., et al. "The Importance of Professional Development in Hairstyling Education." \emph{Revue Française de Pédagogie}, 2023. doi:10.4000/RFP.4225.
\item
  Later. "Marketing Platform for Instagram, TikTok, and More." 2023. \url{https://later.com/}.
\item
  Leblanc, Marie. \emph{Salon Sanitation: A Guide to Hygiene Practices}. Milady, 2020.
\item
  Leighton, A. "Reflections on Mentorship." {[}Video{]}. YouTube, February 12, 2023. \url{https://www.youtube.com/watch?v=8Zy3xQWvZfk}.
\item
  LinkedIn Learning. "How to Evaluate Online Courses." 2023. \url{https://www.linkedin.com/learning}.
\item
  LinkedIn. "Beauty Revolution: AI\textquotesingle s Impact on the Cosmetic Industry." 2023. \url{https://www.linkedin.com/pulse/beauty-revolution-ais-impact-cosmetic-industry}.
\item
  Ling, W.K., et al. "Examining the Effects of Weekly Massage on Occupational Burnout Among Hairstylists." \emph{Journal of Massage \& Bodywork Therapies}, 2(3), 2020: 216-229.
\item
  L\textquotesingle Oréal. "Augmented Reality Makeup Apps." n.d. \url{https://www.lorealparisusa.com/beauty-magazine/makeup/augmented-reality-makeup-apps.aspx}.
\item
  L\textquotesingle Oréal. "Revolutionizing Beauty: AI-Driven Product Innovation." \emph{Harvard Business Review}, June 2020. \url{https://hbr.org/2020/06/ai-in-beauty}.
\item
  L\textquotesingle Oréal. "The Role of AI in Modern Beauty." 2021. \url{https://www.loreal.com/en/innovation/ai-beauty}.
\item
  Mane Choice, The. "About Us." n.d. \url{https://themanechoice.com/pages/about-us}.
\item
  Manning, Jodi. "Hair Symbolism among College Students." \emph{Journal of Folklore Research}, vol. 10, no. 1, 2023. doi:10.5325/jafrireli.10.1.0020.
\item
  Manns-James, L., and A. Neal-Barnett. "Culturally Informed Hair Cortisol Sampling: A Community Engagement Perspective." \emph{Journal of Dermatological Science}, 2023. doi:10.1111/jdv.13642.
\item
  Margolis, E. "The Rise of Vernon François." \emph{Black Beauty Mag}, 2023.
\item
  Mascola, Toni. \emph{The Fundamentals of Hairstyling}. Cengage Learning, 2018.
\item
  McKinsey \& Company. "The Beauty Industry in the Age of COVID-19." 2020. \url{https://www.mckinsey.com/industries/beauty}.
\item
  Meldrum, A. "The Benefits of Automated Credit Card Payments for Small Businesses." \emph{Forbes}, 2021. \url{https://www.forbes.com/sites/forbestechcouncil/2021/06/24/the-benefits-of-automated-credit-card-payments-for-small-businesses/}.
\item
  Mendl, U. "Interview with Elle Magazine." \emph{Elle Magazine}, March 14, 2023.
\item
  Mensah, Charlotte. \emph{Good Hair}. 2020. \url{https://www.goodhairbook.com}.
\item
  Mercer, Kobena. \emph{Welcome to the Jungle: New Positions in Black Cultural Studies}. London: Routledge, 1994.
\item
  Metropolitan Museum of Art, The. "Hair and Wigs in Ancient Egypt." Accessed March 8, 2025. \url{https://www.metmuseum.org/toah/hd/hair/hd_hair.htm}.
\item
  Michele, K. "Trichology: The Science of Healthy Hair." \emph{Modern Salon}, 2023. \url{https://www.modernsalon.com/trichology-science-healthy-hair}.
\item
  Mielle Organics. "About Us." n.d. \url{https://www.mielleorganics.com/pages/about-us}.
\item
  Mielle Organics. "Our Product Philosophy: Moisture \& Healing." 2021. \url{https://www.mielleorganics.com/our-story}.
\item
  Mielle Organics. "Our Story: Celebrating Natural Beauty." 2021. \url{https://www.mielleorganics.com}.
\item
  Milan. "Thank You Note Service." 2023. \url{https://www.milannotes.com/}.
\item
  Milner, N. "Ergonomics for Hairstylists." Salon Safety Inc., December 1, 2020. \url{https://salonsafetyinc.com/ergonomics-for-hairstylists/}.
\item
  MINDBODY. "The Rise of Online Consultations in the Beauty Industry." 2022. \url{https://www.mindbodyonline.com/business/education/blog/online-consultations-beauty-industry}.
\item
  Miu Miu. "Miu Miu ANDAM Fashion Avatars by AI." n.d. \url{https://www.miumiu.com/en/experiences/miu-miu-andam-fashion-avatars-by-ai}.
\item
  Miyamoto, M. \emph{The Artist\textquotesingle s Meditation: Unlocking Presence and Perception}. Shambhala Publications, 2019.
\item
  Modern Salon. "Nick Stenson\textquotesingle s Suburban Networking Strategies." 2020. \url{https://www.modernsalon.com/article/2020/06/nick-stenson}.
\item
  Modern Salon. "Pricing Guide for Professional Hair Tools." 2021. \url{https://www.modernsalon.com/pricing-guide}.
\item
  Modern Salon. "Pricing Strategies for Salon Owners." 2022. \url{https://www.modernsalon.com/pricing-strategies}.
\item
  Modern Salon. "Revenue Diversification Strategies for Freelancers." 2021. \url{https://www.modernsalon.com/revenue-diversification}.
\item
  Modern Salon. "Tabatha Takes Over: How Self-Care Powers High-Profile Stylists." November 20, 2015. \url{https://www.modernsalon.com/tabatha-takes-over-self-care}.
\item
  ModiFace. "Augmented Reality in Beauty: Transforming Client Consultations." 2020. \url{https://www.modiface.com}.
\item
  ModiFace. "Home." n.d. \url{https://www.modiface.com/}.
\item
  Morency, C. "How Jen Atkin Became the Most Influential Hair Stylist in the World." \emph{The Cut}, 2021.
\item
  Msalon.us. "Hair Care for All: Diversity and Inclusivity." 2023. \url{https://www.msalon.us/hair-care-for-all-diversity-and-inclusivity}.
\item
  Murray, D. "Investors Worth \$12B Divest from Lechowicz Enterprises Over Environmental Negligence." \emph{Environmental Finance}, March 10, 2023. \url{https://www.environmental-finance.com/}.
\item
  MyDigiSalon. "Digital Marketing Strategies for Beauty Salon." 2023. \url{https://www.mydigisalon.com/blog/digital-marketing-strategies-beauty-salon/}.
\item
  NAHA. "North American Hairstyling Awards." 2022. Accessed March 8, 2025. \url{https://www.nahaawards.com}.
\item
  National Affordable Housing Act (NAHA). "NAHA Lobby Day Wins Earned Sick Leave Act." July 18, 2021. \url{https://theprobeau.com/naha-lobby-day-2021/}.
\item
  National Institutes of Health. "Hair Biology: Cultural and Genetic Diversity in Hair Structure." 2018. Accessed March 8, 2025. \url{https://www.nih.gov/hair-biology}.
\item
  NaturallyCurly. "Curl Typing System." n.d. Accessed March 8, 2025. \url{https://www.naturallycurly.com/curltyping}.
\item
  NaturallyCurly. "The NaturallyCurly Texture Typing System." 1998. \url{https://www.naturallycurly.com/texture-typing}.
\item
  Naturtint. "Naturtint: Natural Hair Color Solutions." 2022. Accessed March 8, 2025. \url{https://www.naturtint.com/about-sustainability}.
\item
  Nelms, Nikki. "Transparency in Beauty: How Clear Pricing Builds Trust." \emph{Modern Salon}, November 20, 2019. Accessed March 8, 2025. \url{https://www.modernsalon.com/transparency-in-beauty-nikki-nelms}.
\item
  New York State Department of Environmental Conservation. "Drug Take Back Act". 2018. \url{https://DEC.NY.gov}.
\item
  New York Times, The. "Redefining Beauty: The Rise of Natural Hair." April 15, 2018. Accessed March 8, 2025. \url{https://www.nytimes.com/2018/04/15/style/natural-hair-beauty}.
\item
  Newman, Daniel. \emph{The Ultimate Guide to Social Media for Business Owners, Professionals, and Entrepreneurs}. Allworth, 2018.
\item
  NFIB Research Center. "2023 Financial Wellness Report: Small Business Financial Wellness." 2023. \url{https://www.nfib.com/financialwellness}.
\item
  Nielsen. "Consumer-Goods\textquotesingle{} Brands That Demonstrate Commitment to Sustainability Outperform Those That Don\textquotesingle t". 2015. \url{https://Nielsen.com}.
\item
  Nielsen. "Global Trust in Advertising Report." 2021. Accessed March 8, 2025. \url{https://www.nielsen.com/us/en/insights/report/2021/global-trust-in-advertising/}.
\item
  Nielsen. "Sustainable and Ethical Consumerism: A Global Perspective." 2022. \url{https://www.nielsen.com/insights/2022/sustainable-and-ethical-consumerism-a-global-perspective/}.
\item
  Nielsen. "The Sustainability Imperative". 2015. \url{https://Nielsen.com}.
\item
  Nutritionist Resource. "Self-Care." 2023. \url{https://www.nutritionist-resource.org.uk/content/self-care.html}.
\item
  NVIDIA. "How AI Is Transforming the Fashion Industry." May 11, 2021. \url{https://blogs.nvidia.com/blog/2021/05/11/ai-generative-models-fashion-design/}.
\item
  Open Influence. "The Diversity and Inclusion Report: Perception in Online Communities." 2022. \url{https://openinfluence.com/diversity-inclusion-report/}.
\item
  OSHA.gov. "Ergonomics for the Prevention of Musculoskeletal Disorders - Guidelines for Hairstyling." 2021. \url{https://www.osha.gov/ergonomics/guidelines/hairstyling}.
\item
  Ouidad. "The Carve and Slice Technique." 2017. Accessed March 8, 2025. \url{https://www.ouidad.com/professionals/curl-cutting}.
\item
  Oyin Handmade. "About Us." n.d. \url{https://www.oyinhandmade.com/about}.
\item
  Palau, Guido. "Interview with Allure Magazine." \emph{Allure Magazine}, July 25, 2019.
\item
  Palau, Guido. \emph{Hair: Guido}. New York: Rizzoli International Publications, 2013.
\item
  Pandey, J., and S. Srivastava. "The Psychological Impact of Hair Aesthetics." \emph{International Archives of Medicine}, vol. 42, no. 11, 2023. doi:10.46607/iamj4211082023.
\item
  Patel, N. "How to Use Automation to Grow Your Business." 2022. \url{https://neilpatel.com/blog/automation-to-grow-business/}.
\item
  Pearce, J. "The Zen of Vernon François." \emph{Essence Hair}, February 23, 2023. \url{https://www.essence.com/hair/vernon-francois-celebrity-hairstylist-profile/}.
\item
  Perfect Corp. "Home." n.d. \url{https://www.perfectcorp.com/}.
\item
  Perfect Corp. "How AR is Revolutionizing Beauty Consultations." 2022. Accessed March 8, 2025. \url{https://www.perfectcorp.com/ar-beauty}.
\item
  Phelpstead, Carl. "Hair in Medieval Icelandic Literature: Constructing Gendered Identities." \emph{Scandinavian Studies}, vol. 85, no. 2, 2023. doi:10.1353/SCD.2013.0019.
\item
  Philanthropy Circuit. "Strategies for Building Sustainable Funding Models for Nonprofit Organizations." 2023. \url{https://philanthropycircuit.org/insights/strategies-for-building-sustainable-funding-models-for-nonprofit-organizations/}.
\item
  Pierce, D. "Networking: Multi-level Marketing Yourself." \emph{Professional Communication and Career Advancement Techniques}, 1999.
\item
  Porter, S. "Tapping Into Your Creative Well." \emph{Modern Salon}, June 6, 2022. \url{https://www.modernsalon.com/643318/tapping-into-your-creative-well}.
\item
  Potts, Z. \emph{Overcoming The Impossible: My Advocacy Journey}. ZPMedia, 2021.
\item
  Powell, D. "The Hairstylist Industry Report 2022." \emph{Muse \& Mustard}, June 2022.
\item
  Precision Nutrition. "Self-Care Strategies That Work." 2023. \url{https://www.precisionnutrition.com/self-care-strategies-that-work}.
\item
  Prempeh, K. "The Cultural Reinterpretation of Hair through the Veil in Accra, Ghana." \emph{Journal of African Religious Studies}, vol. 10, no. 1, 2023. doi:10.5325/jafrireli.10.1.0020.
\item
  Professional Beauty Association. "Interview with Mark Townsend on Introvert Networking." n.d. Accessed March 8, 2025. \url{https://www.probeauty.org}.
\item
  Project Management Institute. \emph{A Guide to the Project Management Body of Knowledge (PMBOK® Guide)}. Newtown Square, PA: Project Management Institute, 2017.
\item
  Quets, A. L. \emph{The Awakened Stylist: A Guide to Igniting Passion and Unleashing Creativity in Your Salon}. AuthorHouse, 2019.
\item
  Ragins, Bernard R., and K. E. Kram, eds. \emph{The Handbook of Mentoring at Work: Theory, Research, and Practice}. Thousand Oaks, CA: Sage Publications, 2007.
\item
  Rahua. "Sustainability." n.d. \url{https://rahua.com/pages/sustainability}.
\item
  Rahua. "Rahua Amazon Beauty." n.d. \url{https://rahua.com}.
\item
  Rao, M. S. "Creating Legacies through Leadership in the Hairstyling Industry." \emph{Human Resource Management International Digest}, vol. 22, no. 4, 2023. doi:10.1108/HRMID-01-2014-0013.
\item
  Reardon, S. "Top 40 Hair Education Podcasts." \emph{BehindTheChair.com}, January 27, 2022. \url{https://behindthechair.com/articles/hair-education-podcasts/}.
\item
  Reyes, Marco. "Editorial Profile: Marco Reyes on Mentorship in High-Fashion Hair." \emph{WWD}, 2018. \url{https://wwd.com/beauty-industry-news/hair/marco-reyes-profile}.
\item
  Reyes, M. "Top 10 Hairstyling Facebook Groups You Should Know." \emph{Colored Curlz Magazine}, March 2023.
\item
  Robinson, J. "The Importance of Mentorship for Creatives." \emph{CreativePro Magazine}, 12(5), 2020: 28-35.
\item
  Rumi, J.D. \emph{The Essential Rumi} (C. Barks, Trans.). San Francisco: HarperCollins, 1995.
\item
  Saitoh, I. \emph{A Method of Plaiting Hair}. IBC Publishing, 2012.
\item
  Salesforce. "Salesforce CRM for Small Businesses." 2023. Accessed March 8, 2025. \url{https://www.salesforce.com}.
\item
  Salon Business Journal. "Cost Efficiency in Salon Equipment: A Comparative Analysis." 2022. \url{https://www.salonbusinessjournal.com/cost-efficiency}.
\item
  Salon Business Journal. "Economic Resilience Strategies for Hairstylists." 2022. Accessed March 8, 2025. \url{https://www.salonbusinessjournal.com}.
\item
  Salon Today. "Building Your Signature Style: Post-Mentorship Strategies." 2021. Accessed March 8, 2025. \url{https://www.salontoday.com}.
\item
  Salon Today. "The Future of the Salon Industry in the Aftermath of COVID-19." n.d. \url{https://www.salontoday.com}.
\item
  Salon Today. "The Rise of Freelance Hairstylists." 2021. Accessed March 8, 2025. \url{https://www.salontoday.com}.
\item
  Sarcos, R. "The Wisdom of Vernon François." \emph{Cutting Edge Styles Magazine}, 14(6), 2021: 28-35.
\item
  Sassoon, V. "Interview with Salon Magazine." \emph{Salon Magazine}, June 1982.
\item
  Sassoon, Vidal, and Michael O\textquotesingle Donnell. \emph{Vidal: The Autobiography}. New York: Macmillan, 2010.
\item
  ScienceDirect. "Environmental Impacts of Salon Waste Management." 2023. \url{https://www.sciencedirect.com/science/article/pii/S0959652615006460}.
\item
  Scrummi. "Environmental Sustainability in the Hairdressing Salon." 2023. \url{https://scrummi.com/blogs/blog/environmental-sustainability-hairdressing-salon}.
\item
  Selfgood. "Mobile Hair Stylist Business Management." 2023. \url{https://selfgood.com/blog/mobile-hair-stylist-business-management}.
\item
  Selfgood. "Start a Freelance Business: Hair Stylist." 2023. \url{https://selfgood.com/blog/start-freelance-business/hair-stylist}.
\item
  Senge, Peter M. \emph{The Fifth Discipline: The Art \& Practice of The Learning Organization}. New York: Doubleday, 1990.
\item
  Sephora. "Sephora Virtual Artist." n.d. \url{https://www.sephora.com/beauty/virtual-artist}.
\item
  Seth, S. "How to Beat Social Isolation as an Artist." \emph{Artwork Archive}, October 14, 2020. \url{https://www.artworkarchive.com/blog/how-to-beat-social-isolation-as-an-artist}.
\item
  ShearShare. "Leadership Tips for Stylists Starting Their Own Business." 2023. \url{https://shearshare.com/blog/leadership-tips-for-stylists-starting-their-own-business/}.
\item
  Shiel, W. "Hairstyling and Its Impact on Societal Presentation and Quality of Life." \emph{Journal of Cosmetic Dermatology}, vol. 6, no. 4, 2023. doi:10.1111/j.1473-2165.2007.00315.x.
\item
  Sill, Lauren. "Vintage Hairstyling Academy." n.d.
\item
  Sinek, Simon. \emph{Start With Why: How Great Leaders Inspire Everyone to Take Action}. New York: Portfolio, 2009. Accessed March 8, 2025. \url{https://www.startwithwhy.com}.
\item
  Small Business. "Code of Ethics for Salon." 2023. \url{https://smallbusiness.chron.com/code-ethics-salon-41760.html}.
\item
  Smarter Salon. "The Importance of Financial Tracking for Salon Owners." 2023. \url{https://www.smartersalon.com/financial-tracking/}.
\item
  Smith, E. E. \emph{The Power of Meaning: Crafting a Life That Matters}. Crown Publishing Group, 2017.
\item
  Smithsonian Magazine. "The Environmental Impact of Beauty Waste." 2022. \url{https://www.smithsonianmag.com/innovation/environmental-impact-beauty-waste-180979401/}.
\item
  Sonkusare, S. "Mindfulness Practices for Hairstylists." \emph{Embodied Living}, 8(2), 2022: 32-41.
\item
  Sonkusare, S. "The Benefits of Breathwork." \emph{Mindful Magazine}, July 21, 2022. \url{https://www.mindful.org/the-benefits-of-breathwork/}.
\item
  Sonthalia, S., et al. "Hair and Psychological Well-being." \emph{Journal of Cosmetic Dermatology}, vol. 1, no. 1, 2023. doi:10.4172/2471-9323.1000E101.
\item
  St. Lawrence College. "Hairstyling and Esthetics." 2023. \url{https://www.stlawrencecollege.ca/community/hairstyling-and-esthetics}.
\item
  Stough, D. B., et al. "Diversity and Inclusion in Hair Transplantation." \emph{Journal of the European Academy of Dermatology and Venereology}, vol. 33, no. 3, 2023. doi:10.1111/jdv.136.
\item
  Streetwise Journal. "How to Become a Hairstylist." 2023. \url{https://streetwisejournal.com/how-to-become-a-hairstylist/}.
\item
  Study Moose. "Effective Leadership in a Hair Salon." 2023. \url{https://studymoose.com/effective-leadership-in-a-hair-salon-essay}.
\item
  Style Academy. "Hairstyling Event, March 23." 2023. \url{https://styleacademy.ca/event/hairstyling-mar-23/}.
\item
  Stylez, T. "The Art of Continuous Evolution." \emph{Behind the Chair}, January 16, 2023. \url{https://behindthechair.com/articles/tokyo-stylez-art-of-continuous-evolution/}.
\item
  Subscription Genius. "Product Sample Subscription Service." 2022. \url{https://www.subscriptiongenius.com/}.
\item
  Sustainable Jungle. "Vegan Hair Products." 2023. \url{https://sustainablejungle.com/best-of-sustainable-beauty/vegan-hair-products/}.
\item
  Sway. "Sway from Microsoft Office." 2022. \url{https://www.microsoft.com/en-us/microsoft-365/online-software/sway}.
\item
  T3 Micro. "Innovative Hair Styling Tools." 2023. \url{https://www.t3micro.com/hair}.
\item
  Teixeira, M. \emph{The Art of Metamorphosis}. Origin Publishers, 2021.
\item
  TextureMedia. "Professional Education for Textured Hair." n.d. Accessed March 8, 2025. \url{https://www.texturemedia.com/education}.
\item
  TextureTalk. "Inclusion in Cosmetology: The Need for Textured Hair Education." 2020. Accessed March 8, 2025. \url{https://www.texturetalk.com/inclusion-cosmetology}.
\item
  The Freelance Hairstylist\textquotesingle s Network. "Facebook group." n.d.
\item
  The Industry Beauty. "The Role of AI and AR in the Beauty Industry." 2023. \url{https://theindustry.beauty/the-role-of-ai-and-ar-in-the-beauty-industry/}.
\item
  Thomas, D. "Ted Gibson\textquotesingle s Journey of Empowering Clients Through Hairstyling." \emph{Essence}, June 20, 2019. \url{https://www.essence.com}.
\item
  Thompson, L. "The Power of Representation in Visual Content." \emph{Vogue Business}, 2021. \url{https://www.voguebusiness.com/marketing/the-power-of-representation-in-visual-content}.
\item
  Times of India. "The Evolution of Beauty: Examining the Impact of AI in the Industry." 2023. \url{https://timesofindia.indiatimes.com/blogs/voices/the-evolution-of-beauty-examining-the-impact-of-ai-in-the-industry/}.
\item
  Together Platform. "What is the Purpose of Mentoring." 2023. \url{https://www.togetherplatform.com/blog/what-is-the-purpose-of-mentoring}.
\item
  Tutorials Point. "Hairstyling Industry." 2023. \url{https://www.tutorialspoint.com/hairstyling-industry}.
\item
  U.S. Chamber of Commerce. "Community Education Opportunities." 2021. Accessed March 8, 2025. \url{https://www.uschamber.com}.
\item
  U.S. Department of Energy. "Energy Efficiency for Small to Medium Businesses". 2021. \url{https://Energy.gov}.
\item
  U.S. Financial Literacy and Education Commission. "Financial Wellness and the Importance of an Emergency Fund." 2016. Accessed March 8, 2025. \url{https://home.treasury.gov/policy-issues/financial-markets-financial-institutions-and-fiscal-service}.
\item
  U.S. Occupational Safety and Health Administration. "Ergonomics for Hairdressers." 2021. Accessed March 8, 2025. \url{https://www.osha.gov/ergonomics/hairdressers}.
\item
  U.S. Occupational Safety and Health Administration. "Ergonomics in the Workplace." 2020. Accessed March 8, 2025. \url{https://www.osha.gov/ergonomics}.
\item
  U.S. Occupational Safety and Health Administration. "Salon Safety and Sanitation Guidelines." 2020. \url{https://www.osha.gov/salon-safety}.
\item
  Udemy. "Online Courses on Hairstyling and Beauty." 2023. \url{https://www.udemy.com/courses/search/?q=hairstyling}.
\item
  Umble, A. "How to Set Better Boundaries at Work During Covid-19." \emph{Forbes}, May 15, 2020. \url{https://www.forbes.com/sites/averyblank/2020/05/15/how-to-set-better-boundaries-at-work/}.
\item
  Umberson, Debra, and Jennifer K. Montez. "Social Relationships and Health: A Flashpoint for Health Policy." \emph{Journal of Health and Social Behavior} 51, suppl. (2010): S54--S66. \url{https://doi.org/10.1177/0022146510383501}.
\item
  UNESCO. "Cultural Heritage and Traditional Skills." 2021. Accessed March 8, 2025. \url{https://en.unesco.org}.
\item
  Unilever. "Unilever partners with AI to accelerate product innovation." May 22, 2019. \url{https://www.unilever.com/news/press-releases/2019/unilever-partners-with-ai-to-accelerate-product-innovation.html}.
\item
  University of Education Network. "Mentoring Case Studies." 2023. \url{https://uen.pressbooks.pub/makingconnections/part/mentoring-case-studies/}.
\item
  Vegamour. "What is Hair Wellness?" 2023. \url{https://vegamour.com/blogs/blog/what-is-hair-wellness}.
\item
  Villa, S. "Sam Villa: Sharing Knowledge \& Leading the Next Generation of Stylists (Interview)." \emph{Modern Salon}, 2015.
\item
  Wauchope, J. "Beauty Unites Communities." {[}Keynote speech transcript{]}. Intercoiffure America/Canada Fall Atelier, Chicago, IL, October 2, 2022.
\item
  Wauchope, J. Personal interview. 2023.
\item
  Welch, L. "The Legendary Guido Palau Breaks Down the Best Hair Looks from the Fall 2022 Runways." \emph{Vogue}, April 5, 2022. \url{https://www.vogue.com/article/guido-palau-best-hair-looks-fall-2022}.
\item
  Welp, A., Fritz, C., \& Radke, M. "Resilience in Healthcare: Fostering Meaning and Purpose Orientation." \emph{Journal of Applied Psychology}, 107(4), 2022: 629-645.
\item
  WomenStrongAlliance. "The Crown Act: Ending Hair Discrimination." 2022. \url{https://www.womenstrongalliance.org/crown-act}.
\item
  Worthington, C. \emph{The Complete Book of Hairstyling}. Thomson Learning, 2001.
\item
  York University. "Technological Education ABQ: Hairstyling and Aesthetics Grades 9 and 10." 2023. \url{https://apps.edu.yorku.ca/pdis/course/technological-education-abq/hairstyling-and-aesthetics-grades-9-and-10/}.
\item
  Zeffane, R. "The Widening Scope of Inter-Organizational Networking." \emph{Economic and Organizational Benefits of Strategic Networking}, 1995.
\item
  Zellmer, M. "Hairstylists Take on Many Emotional Support Roles, Which Can Be Draining." \emph{Philadelphia Inquirer}, August 12, 2020. \url{https://www.inquirer.com/life/hairstylists-emotional-support-20200812.html}.
\item
  Zito, R. "Finding Joy in the Everyday." \emph{Passion Hairbible}, 22(5), August 2021: 108-110.
\end{itemize}

This bibliography represents a curated selection of resources to support your ongoing journey.
